\documentclass[10pt]{article}
\usepackage[a4paper,margin=0.85in]{geometry}
\usepackage{hyperref}
\usepackage{textcomp}
\begin{document}
\begin{titlepage}
\thispagestyle{empty}
\small
\begin{center}
{\Large\bfseries Title Page}\\[0.7em]
{Engineering with Computers -- Original Article}\\[1.0em]
{\LARGE\bfseries A GA-Warm-Started Mixed-Integer Nonlinear Framework for Discrete IS~800-Compliant Space-Truss Optimization}\\[0.5em]
{\footnotesize Short title: A GA-warm-started MINLP framework for code-constrained truss optimization}
\end{center}

\vspace{0.7em}
\noindent\textbf{Authors:} First Author\textsuperscript{1,*} and Second Author\textsuperscript{1}\\
\textbf{Affiliation:} \textsuperscript{1}Department of Civil Engineering, Institute/University Name, City, State, India.\\
\textbf{Corresponding author:} First Author; \texttt{corresponding.author@example.com}\\
\textbf{Contributing author:} Second Author; \texttt{second.author@example.com}\\
\textbf{ORCID IDs:} First Author: [ORCID ID]; Second Author: [ORCID ID]

\vspace{0.7em}
\noindent\textbf{Acknowledgements.} The authors gratefully acknowledge the computational support provided by the Department of Civil Engineering.

\vspace{0.45em}
\noindent\textbf{Funding.} The authors received no specific funding for this work. Update this statement if any institutional, government, or project funding supported the study.

\vspace{0.45em}
\noindent\textbf{Author contributions.} Author 1: Conceptualisation, methodology, software, validation, formal analysis, visualization, and writing--original draft. Author 2: Supervision, methodology review, validation review, and writing--review and editing.

\vspace{0.45em}
\noindent\textbf{Competing interests.} The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

\vspace{0.45em}
\noindent\textbf{Ethics approval and consent to participate.} Not applicable.

\vspace{0.45em}
\noindent\textbf{Consent for publication.} Not applicable.

\vspace{0.45em}
\noindent\textbf{Data availability.} The benchmark definitions, SP~6(1):1964 section catalogue data, seed-fixed optimization results, and post-processing files required to reproduce the tables and figures are openly available in the archived Zenodo release at \url{https://doi.org/10.5281/zenodo.20508136}. The active source repository is available at \url{https://github.com/mdaipayan/GA-MINLP-IS800-Truss-Optimization}.

\vspace{0.45em}
\noindent\textbf{Code availability.} The Python implementation used for the direct-stiffness analysis, IS~800:2007 member checks, optimization algorithms, statistical runs, and figure/table generation is available at \url{https://github.com/mdaipayan/GA-MINLP-IS800-Truss-Optimization} and archived with the reproducibility package at \url{https://doi.org/10.5281/zenodo.20508136}.

\vspace{0.45em}
\noindent\textbf{Use of AI-assisted technologies.} During the preparation of this manuscript, the authors used Claude (Anthropic) and ChatGPT (OpenAI) to assist with \LaTeX{} formatting, language editing, manuscript organisation, and journal-specific wording. The authors reviewed and edited all AI-assisted content and take full responsibility for the scientific accuracy and integrity of the work.

\vfill
\noindent\textit{Author action before submission: replace all placeholder names, emails, affiliation, and ORCID IDs.}
\end{titlepage}

\end{document}
